Viscous Transport in Eroding Porous Media

### 2020-01-27 docs/transport/Response_to_Reviewer_2.tex

  \item There were other instances in the paper where we claimed to be
    performing an `experiment'. We have clarified each of the instances
    by referring to them as a `numerical experiment'.
\end{itemize}

\noindent
\comment{sections 6.2 and 6.3.  How were these geometries of 20 grains
chosen?  Both the sizes and positions of these grains vary between
examples - it's not just the porosity that is different.}
\begin{itemize}
  \item The initial placement and radii of the bodies are chosen with a
    randomized method. The algorithm is descried at the start of Section
    6.

  \item We have updated the start of section 6.2 to read:
    \begin{quotation}
      \noindent
      We randomly initialize 20 eroding grains with an initial porosity
      of $\phi = 37.68\%$ and the Hagen-Poiseuille flow
      $\mathbf{U}(\mathbf{x}) = U (1-y^2, 0)$ imposed on $\Gamma$.
    \end{quotation}

  \item We have updated the start of section 6.3 to read:
    \begin{quotation}
      \noindent
      We consider a second example with 20 randomly initialized eroding
      bodies, but with a smaller initial porosity of $\phi = 30.67\%$.
    \end{quotation}

@@

\noindent
\comment{Figure 8.  Due to what I presume is an artifact of plotting, it
looks like lots of streamlines suddenly end, which is confusing.}
\begin{itemize}
  \item In figure 8, we freeze an eroded geometry and plot the
    trajectory of passive tracers at five different time steps. Since
    the flow is steady and the tracers are passive, the trajectories
    trace out streamlines.

  \item We have updated the caption to read:
    \begin{quotation}
      \noindent
      200 particle trajectories in the second geometry from figure 6.
      The particles are initially equispaced at $(−1,y)$, where $y \in
      (-1, 1)$. The first five snapshots are equispaced in time. The
      bottom right frame is a magnification of the fifth snapshot, but
      with additional trajectories.
    \end{quotation}

  \item We have also updated the paragraph describing figure 8 to
    clarify that it is showing tracer trajectories that trace out
    streamlines.
\end{itemize}

\noindent
\comment{Figure 9.  While the sharp features in subfigure (b) are
apparently finite cusps, they raise the question of whether any infinite
dwell times (divergent $\tau$) are ever observed in these simulations -
i.e.~are particles ever trapped inside recirculating zones?}
\begin{itemize}
  \item Thank you for pointing out this possibility. The
    recirculation zones are close to the eroding bodies and are
    typically very small. Because we measure the local tortuosity by
    initiating tracers significantly far from the grains, each of them
    connect the inlet to the outlet.

### 2020-01-27 docs/transport/Response_to_Reviewer_3.tex

\begin{document}

\noindent
Dear Silas Alben,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments.  The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript.  We also note that formatting
issues were resolved in the bibliography, and minor grammatical errors
were corrected throughout. An itemized list of the changes addressing
the reviewer's comments are below.  \\ \\
\noindent
Sincerely,
\\
\noindent
Shang-Huan Chiu, Nick Moore, and Bryan Quaife

\section*{Response to Reviewer 3}

\noindent
\comment{Pores in natural porous media care of three-dimensional
geometry.  The authors may include some discussion on how to extend
their numerical method to three-dimensional problems.  In addition, they
may also discuss the limitations of the erosion analysis in
2-dimensional flow to be applied for three-dimensional flow. If the
erosion process in three-dimensional flow is very different from that in
two-dimensional flow, the analysis of this paper may have less relevant
to the analysis of erosion in natural porous media.}
\begin{itemize}
  \item The reviewer is correct that by assuming the geometry is
    two-dimensional, we have limited the applicability for natural
    porous media. There are several numerical challenges to simulate
    three-dimensional erosion, with the most significant being the
    $\theta$--$L$ formulation, quadrature methods, spectral
    representations of the geometry, and the boundary integral equation
    solver.

  \item In three-dimensions, others have developed methods to extend the
    $\theta$--$L$ formulation to remove stiffness in interfacial flow,
    spectrally represented geometries, and efficiently solve BIEs.  The
    challenge with these methods is their computational cost. To
    consider suspensions with the resolution and number of grains that
    we consider, the BIE would most likely require a parallel
    implementation that would run on high-performance computing
    architectures. At this point, this is not the goal of our work.
    Rather, we are interested in using very high-order methods to
    provide an analysis of the effects of erosion on transport which
    seems to be missing from the literature.
